IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
Directly, the label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%
(For these rules, we assume that the |Lb| constructor is not part of
the surface syntax and thus cannot be accessed directly to construct
or destruct such values without label checks.)
% 
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%}

@@

\paragraph{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
Since both the LIO and SWAPI implementations already support such features,
we believe that extending our calculus to consider privileges is
straight forward.
%
However, the challenge with such an extension lies in the precise
security guarantees that must be proved.
%
Addressing this problem is a natural direction for this work.

@@

\subsection{Scheduling policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
  considerably more complex. See~\cite{Kashyap:2011}.
}
%
More generally, we believe that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%
We leave the proof of this claim to future work.
%

>>>>

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
The label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%
(For these rules, we assume that the |Lb| constructor is not part of
the surface syntax and thus cannot be accessed directly to construct
or destruct such values without label checks.)
% 
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%}

@@

\paragraph{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
Since both the LIO and SWAPI implementations already support such features,
we believe that extending our calculus to consider privileges is
straight forward.
%
However, the challenge with such an extension lies in the precise
security guarantees that must be proved.
%
%Addressing this problem is a natural direction for this work.

@@

\subsection{Scheduling policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
  considerably more complex. See~\cite{Kashyap:2011}.
}
%
More generally, we believe that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%

### 2014-03-02 paper/formal.tex

The definition of |erasef il| is quite important, as it captures the IFC
language's attacker model: elements that are erased cannot be observed
by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\tocite{}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\tocite{}.
  %
  We leave this extension to future work.
}

>>>>

The definition of |erasef il| is quite important, as it captures the IFC
language's attacker model: elements that are erased cannot be observed
by the attacker.
%
In our case, we assume that the attacker cannot observe sensitive tasks or
messages, or even the number of such entities.
%
While such assumptions are standard~\cite{Castellani:Boudol:ICALP01,
stefan:addressing-covert}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\cite{yangresource}.
  %
  We leave this extension to future work.
}

### 2014-03-02 paper/proofs.tex

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
    respectively, don't get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  this
    is true even with arbitrary additional premises $P$ that follow
    the condition in Definition~\ref{def:restricted}, since those
    predicates only depend on |erase il ic1|, which is equivalent
    to |erase il ic2|, and thus those predicates evaluate in the same way.
    Thus, we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il|-equivalent).
    Again, only sending and receiving will depend on, or change |iS|,
    so we consider all these cases.
    \begin{description}
      \item[Case \textsc{I-send}]
      Here, the task |it2| will send the same message to the same
      receiver queue. This
      queue is either completely erased, or it is |il|-equivalent.  In both
      cases, |il|-equivalence of |iS1'| and |iS2'| is preserved.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      When the tasks are receiving a message, then by the reduction rules
      we know that they first filter the queue by the label
      |lcurr| of |it1|.  We
      also know that the queues are equivalent when filtered by the less
      restrictive label |il|, thus the messages received (or dropped) from the
      queue are equivalent.
    \end{description}
  \end{itemize}
\end{proof}
The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\tocite{} for a TINI proof of a similar system).

>>>>

    Therefore, after |ic2| has potentially executed some number of steps
    to arrive at |ic2''|, we are now in the situation where $|ic1|\approx_{|il|}|ic2''|$, and the first tasks |it1| and |it2|,
    respectively, don't get erased and are thus equivalent.
    The task |it2| can now take exactly the same step as |it1|;  this
    is true even with arbitrary additional premises $P$ that follow
    the condition in Definition~\ref{def:restricted}, since those
    predicates only depend on |erase il ic1|, which is equivalent
    to |erase il ic2|, and thus those predicates evaluate in the same way.
    Thus, we only
    need to argue that the potential differences in |iS1| and |iS2| cannot
    have an influence on the execution (and we know |iS1| and |iS2| are
    |il|-equivalent).
    Again, only sending and receiving will depend on, or change |iS|,
    so we consider all these cases.
    \begin{description}
      \item[Case \textsc{I-send}]
      Here, the task |it2| will send the same message to the same
      receiver queue. This
      queue is either completely erased, or it is |il|-equivalent.  In both
      cases, |il|-equivalence of |iS1'| and |iS2'| is preserved.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      When the tasks are receiving a message, then by the reduction rules
      we know that they first filter the queue by the label
      |lcurr| of |it1|.  We
      also know that the queues are equivalent when filtered by the less
      restrictive label |il|, thus the messages received (or dropped) from the
      queue are equivalent.
    \end{description}
  \end{itemize}
\end{proof}
The proof of Theorem~\ref{thm:iso-tini} about TINI proceeds largely
in the same fashion as for Theorem~\ref{thm:iso-tsni} (TSNI), except that
some cases are simpler due to the fact termination is not an issue
(cf.~\cite{lio} for a TINI proof of a similar system).
